\documentclass[10pt, letterpaper]{letter}
\usepackage{fullpage}
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{mathabx}
%\usepackage{enumitem}
%\usepackage{graphicx}
%\usepackage{multicol}
%\usepackage{mathtools}
%\usepackage{verbatim}
%\usepackage{wasysym}

\setlength{\parindent}{0pt}
\setlength{\parskip}{\baselineskip}

%\newcommand{\cP}{\mathcal{P}}
%\newcommand{\N}{\mathbb{N}}
%\newcommand{\Z}{\mathbb{Z}}
%\newcommand{\R}{\mathbb{R}}
%\newcommand{\C}{\mathbb{C}}

%\newcommand{\p}[1]{\left(#1\right)}
%\newcommand{\pfrac}[2]{\left(\frac{#1}{#2}\right)}
%\newcommand{\set}[1]{\left\{#1\right\}}\usepackage{amsmath}




\begin{document} 
%\setlength{\abovedisplayskip}{6pt}
%\setlength{\belowdisplayskip}{6pt}
%\setlength{\abovedisplayshortskip}{6pt}
%\setlength{\belowdisplayshortskip}{6pt}

\begin{flushright} 
Kevin Ji \\
6534 Old Chesterbrook Road \\
McLean, VA 22101 \\
kwji@email.wm.edu \\
(571)-215-8708
%\\[\baselineskip]

February 3, 2014
\end{flushright}

Dear Hiring Manager,

Please accept my resume for consideration for the position of software engineer. I heard about this position through my brother, Jason Ji, currently a software developer at MITRE. I believe that my skills and experience make me well suited to excel at your company.

I am currently a software developer with CGI Federal, working to implement the Federally Facilitated Marketplace (Healthcare.gov). For the past eight months, I have worked with multiple teams to implement critical back-end functionality and to improve system performance and stability. In the months leading up to the October release, I implemented a large scale content reprocessing function to extract insurance plan data from the Plan Management database and reprocess it into a consumable format for the financial managment system. This data is critical for computing cost share reduction values for each Healthcare.gov user. After the system went live, I joined the Plan Compare team to design and implement a new system-wide caching scheme which improved the average system response time from over 12 seconds to approximately 350 milliseconds. This also substantially reduced the average load on our database and improved the system failure rate. I also helped to resolve defects with and implement improvements for the rating engine component which is responsible for computing the eligible plans, monthly premiums, deductibles, and benefits which are displayed to the users while shopping for healthcare. In particular, I resolved a large number of high-profile defects including missing plans, and rates and deductibles computed incorrectly by hundreds or even thousands of dollars. 

%\textbf{Some blurb about being a recent college graduate and a summary of what I got from there... maybe put this below the next paragraph}

I have enjoyed working on Healthcare.gov immensely. It has been tremendously exciting and a phenomenal learning experience. However, because CGI's contract for work on Heathcare.gov was not renewed by CMS, my future with CGI is now uncertain. My brother has told me a great deal about his software development work with MITRE and I would be extremely interested in joining your company. While I have enjoyed my time with CGI, I would like to work on projects which are closer to the cutting edge and more research oriented, and I look forward to the intellectual challenge that will accompany this type of work. I'm also excited to work with smaller and more agile teams where I can make a greater contribution and continue to serve the federal government. Given MITRE's culture and research focus, I feel that this would be a perfect fit. 

%\textbf{I just plagerized this from you...} 
The enclosed resume provides details about my skills and experience. I believe my experience as a developer on the Federally Facilitated Marketplace as well as my background in computer science and mathematics in college have provided me with invaluable skills which will allow me to excel as a software engineer at MITRE. Thank you for your time and consideration; I look forward to hearing from you soon. 

Sincerely,

Kevin Ji

\end{document}